When are Fuzzy Extractors Possible?

### 2014-06-04 info-bounds/FuzzyExtPossibility.tex
putting in universal hash construction

\section{Well-spread distributions}
We will start with an intuitively simple type of distribution where no results are known.  Security should be easy when all points of $W$ are far apart.  Intuitively, the fuzzy extractor/secure sketch does not need to disambiguate points and thus error-correction should be easy.  Indeed for any error-correcting code, a fuzzy extractor can be designed~(where the design of the fuzzy extractor depends on the supported distribution).  However, this intuition becomes more difficult when a fuzzy extractor should work for all well-spread distributions.  We begin by defining a well-spread distribution.

@@

\begin{lemma}
Let $W$ be a $t_{sec}$ well-spread distribution with $\Hoo(W)\ge k$ there exists a $(\mathcal{M}, m, m, t_{sec}/2)$-secure sketch with no error that works for $W$.  In particular, $\sketch(w) = \perp$, and $\rec(w')$ finds the nearest $w\in W$.  \rec is efficient if there exists efficient decoding for the points in $W$.  By \lemref{lem:fuzzy ext construction} there also exists a fuzzy extractor.\bnote{fill in the parameters}
\end{lemma}

Ideally, a fuzzy extractor should work for any distribution~(or at least a large family of distributions).  However, as we show below the above construction does not extend to the setting of all well-spread distributions.  In particular, any secure sketch must write down a large number of bits~(matching our known constructions of secure sketches).  However, it is not known if it is necessary to decrease the entropy of the distribution $W$.

\begin{lemma}
Let $\mathcal{W}$ be the set of all $t_{sec}$-well spread distributions.  Let $(\sketch, \rec)$ be a $(\mathcal{M}, m, \tilde{m}, t_{cor})$-secure sketch.  Then the length of $\sketch$ is at least $\log |B_{t}|$.
\end{lemma}
\begin{proof}
Let $\mathcal{M}$ be a metric space.
Let $\mathcal{W}$ be the set of all $t_{sec}$-well spread distributions on $\mathcal{M}$.  
Consider the following experiment:
\[
W\leftarrow \mathcal{W} \wedge w \leftarrow W \wedge w'\leftarrow B_{t_{sec}}(w) \wedge ss \leftarrow \sketch(w) \wedge w^* \leftarrow \rec(w', ss).
\]
Since $(\sketch, \rec)$ works for any well-spread distribution the $\Pr[w^* = w] =1 $ in the above experiment.   Denote by $X$ the joint distribution of $w, w'$ produced in the above experiment.  Now consider the following experiment
\[
v \leftarrow U_{\mathcal{M}} \wedge v'\leftarrow B_{t_{sec}}(v) \wedge ss \leftarrow \sketch(v) \wedge v^* \leftarrow \rec(v', ss).
\]
Denote by $Y$ the joint distribution of $v, v'$ produced in the above experiment.  Then $X\overset{d}= Y$.  That is, the view of $(\sketch, \rec)$ is identically distributed in both cases.  Thus, $\Pr[v^* = v] = 1$.  For the uniform distribution the entropy retained by a secure sketch is at most $\Hav(U_{\mathcal{M}} | \sketch(U_{\mathcal{M}})) \le \log |\mathcal{M} - \log |B_t(\cdot)|$~\cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08}.  For a secure sketch to lose $\log |B_{t_{sec}}(\cdot)|$ bits of entropy it must write down at least $\log |B_{t_{sec}}(\cdot)|$ bits~\cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}.  Thus, $(\sketch, \rec)$ writes down at least $\log |B_{t_{sec}}|$ bits on the uniform distribution and its view is identical on $X$ so it writes down at least $\log |B_{t_{sec}}|$ bits on $X$.  This completes the proof.\bnote{need to deal with the case where the number of bits written by $\sketch$ is variable.}
\end{proof}
\bibliographystyle{alpha}
\bibliography{crypto}

>>>>

\section{Well-spread distributions}
\subsection{Depends on Distribution}
We will start with an intuitively simple type of distribution where no results are known.  Security should be easy when all points of $W$ are far apart.  Intuitively, the fuzzy extractor/secure sketch does not need to disambiguate points and thus error-correction should be easy.  Indeed for any error-correcting code, a fuzzy extractor can be designed~(where the design of the fuzzy extractor depends on the supported distribution).  However, this intuition becomes more difficult when a fuzzy extractor should work for all well-spread distributions.  We begin by defining a well-spread distribution.

@@

\begin{lemma}
\label{lem:nosketchwellspread}
Let $W$ be a $t_{sec}$ well-spread distribution with $\Hoo(W)\ge k$ there exists a $(\mathcal{M}, m, m, t_{sec}/2)$-secure sketch with no error that works for $W$.  In particular, $\sketch(w) = \perp$, and $\rec(w')$ finds the nearest $w\in W$.  \rec is efficient if there exists efficient decoding for the points in $W$.  By \lemref{lem:fuzzy ext construction} there also exists a fuzzy extractor.\bnote{fill in the parameters}
\end{lemma}

\subsection{Works for all well-spread distributions}
Ideally, a fuzzy extractor should work for any distribution~(or at least a large family of distributions).  However, as we show below the above construction does not extend to the setting of all well-spread distributions.  In particular, any secure sketch must write down a large number of bits~(matching our known constructions of secure sketches).  However, it is not known if it is necessary to decrease the entropy of the distribution $W$.

\begin{lemma}
Let $\mathcal{W}$ be the set of all $t_{sec}$-well spread distributions.  Let $(\sketch, \rec)$ be a $(\mathcal{M}, m, \tilde{m}, t_{cor})$-secure sketch.  Then the length of $\sketch$ is at least $\log |B_{t}|$.
\end{lemma}
\begin{proof}
Let $\mathcal{M}$ be a metric space.
Let $\mathcal{W}$ be the set of all $t_{sec}$-well spread distributions on $\mathcal{M}$.  
Consider the following experiment:
\[
W\leftarrow \mathcal{W} \wedge w \leftarrow W \wedge w'\leftarrow B_{t_{sec}}(w) \wedge ss \leftarrow \sketch(w) \wedge w^* \leftarrow \rec(w', ss).
\]
Since $(\sketch, \rec)$ works for any well-spread distribution the $\Pr[w^* = w] =1 $ in the above experiment.   Denote by $X$ the joint distribution of $w, w'$ produced in the above experiment.  Now consider the following experiment
\[
v \leftarrow U_{\mathcal{M}} \wedge v'\leftarrow B_{t_{sec}}(v) \wedge ss \leftarrow \sketch(v) \wedge v^* \leftarrow \rec(v', ss).
\]
Denote by $Y$ the joint distribution of $v, v'$ produced in the above experiment.  Then $X\overset{d}= Y$.  That is, the view of $(\sketch, \rec)$ is identically distributed in both cases.  Thus, $\Pr[v^* = v] = 1$.  For the uniform distribution the entropy retained by a secure sketch is at most $\Hav(U_{\mathcal{M}} | \sketch(U_{\mathcal{M}})) \le \log |\mathcal{M} - \log |B_t(\cdot)|$~\cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08}.  For a secure sketch to lose $\log |B_{t_{sec}}(\cdot)|$ bits of entropy it must write down at least $\log |B_{t_{sec}}(\cdot)|$ bits~\cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}.  Thus, $(\sketch, \rec)$ writes down at least $\log |B_{t_{sec}}|$ bits on the uniform distribution and its view is identical on $X$ so it writes down at least $\log |B_{t_{sec}}|$ bits on $X$.  This completes the proof.\bnote{need to deal with the case where the number of bits written by $\sketch$ is variable.}
\end{proof}

\section{Non-well spread distributions}
\subsection{Dependence on Distributions}
\lemref{lem:nosketchwellspread} showed that if a fuzzy extractor~(resp. secure sketch) is built for a particular well-spread distribution, it is not necessary to write down information-reconciliation information.  In this section, we consider information-theoretic bounds on distributions that contain multiple points in each ball.  We start by considering distributions that have a fixed number of neighbors for each point.

\begin{definition}
We call a distribution $W$, over metric space $\mathcal{M}$, $(c, t)$-\emph{fixed neighbor} if there exists a constant $c$ such that for all points in $x\in \mathcal{M}$ there are exactly $c$ points $w\in W$ such that $\dis(w, x)\le t$.  We say that $W$ is a $(c, t)$-\emph{bounded neighbor distribution} if for all point $x\in\mathcal{M}$ there are at most $c$ points $w\in W$ such that $\dis(w, x)\le t$.
\end{definition}

\textbf{Note:} A fixed neighbor distribution is a special case of a bounded-neighbor distribution.

We now present an information-theoretic construction for fixed-neighbor distributions.  We first introduce the notion of a pairwise-independent hash:

\begin{definition}
Let $F : \mathcal{K} \times D \to R$ be a function.  We say that $F$ is \emph{universal} if for all distinct $x_1, x_2 \in D$:
\[
 \Pr_{K \leftarrow \mathcal{K}}[F(K, x_1) = F(K, x_2)] = \frac{1}{|R|} \;.
\]
In other words, $F(K,x_1),F(K,x_2)$ are all uniformly and independently random over $R$. 
\end{definition}

We now show a sufficiently-long universal hash function suffices to construct an information-theoretic fuzzy extractor.

\begin{construction}
\label{cons:pairwise hash}
Let $W$ be a $(c, t)$-fixed neighbor distribution over $\mathcal{M}$.  Let $F :\mathcal{M}\times \mathcal{M}\rightarrow R$ be a pairwise independent hash function.  We describe $\sketch, \rec$ as follows:
\begin{itemize}
\item $\sketch(w)$:
\subitem Sample $K\leftarrow \mathcal{K}$.
\subitem Set $p = F(K, w), K$.
\item $\rec(w', y, K)$:
\subitem Enumerate $W^* = \{w \in W | \dis(w, w')\le t\}$.
\subitem For all $w^*\in W^*$, if $F(K, w^*) = y$, output $w^*$.
\subitem Output $\perp$.
\end{itemize}
\end{construction}
\begin{lemma}
\consref{cons:pairwise hash} is a $(\mathcal{M}, m, m - \log |R|, t)$-secure sketch with error $\delta = \frac{c-1}{|R|}$. 
\end{lemma}
\begin{proof}
We first argue security.  Since $\mathcal{K}$ and $W$ are independent $\Hav(W | \mathcal{K}) = \Hoo(W) = m$.  Then by \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}, $\Hav(W | \mathcal{K}, F(K, W)) \ge \Hoo(W) - \log |F(K, W)| \ge m - \log |R|$.

We now argue correctness.  Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$ recall that the size of $W^*$ is $c$ and since $w, w'$ are chosen independently of $\sketch$ this set is independent of the choice of $\mathcal{K}$.  Note $\rec$ will never output $\perp$ as the correct $w$ will match the hash, our goal is to bound the probability that another element $w^*$ collides, that is $F(K, w^*) = F(K, w)$.
\begin{align*}
\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] \le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)]  = \frac{c-1}{|R|}
\end{align*}
Where the inequality proceeds by union bound and the equality proceeds by the universality of $F$.  This completes the proof.
\end{proof}
\begin{corollary}
Let $n$ be a security parameter.  
If $|R| \ge c * n^{\omega(1)}$ then \consref{cons:pairwise hash} is correct with overwhelming probability.  That is, setting $\log |R| = \log |c| + \omega(\log n)$ suffices.
\end{corollary}

\bibliographystyle{alpha}
\bibliography{crypto}
